Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-13 tex/VHzQ.tex
CFHQSJ0216-0455LC update

\begin{figure}
  \begin{subfigure}{}
    \centering
    \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190214.png}
    \caption{The infrared light curve for MMT J0215-0529 with data from 
      WFCAM (smaller solid circles), VIRCAM (hexagons) and NEOWISE-R (larger solid circles).
MMT  J0215-0529 was identified by \citet{McGreer2018}, 
% 02:15:23.27 −05:29:45.8
%g_AB = 28.05 \pm 1.00 
%r_AB = 22.69 \pm  0.01
%           20.85 \pm  0.01 
%           20.64 \pm 0.01
% −25.7 5.13 MMT 
}
    \label{fig:MMTJ0215-0529}
  \end{subfigure} 
  \begin{subfigure}{}
    \centering
    \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190214.png}
    \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for CFHQS J0216-0455.}
    \label{fig:CFHQSJ0216-0455}
  \end{subfigure}
\end{figure}

>>>>

\begin{figure}
  \begin{subfigure}{}
    \centering
    \includegraphics[width=8.5cm]{../light_curves/MMTJ0215-0529LC_20190613.png}
    \caption{The infrared light curve for MMT J0215-0529 with data from 
      WFCAM (smaller solid circles), VIRCAM (hexagons) and NEOWISE-R (larger solid circles).
MMT  J0215-0529 was identified by \citet{McGreer2018}, 
% 02:15:23.27 −05:29:45.8
%g_AB = 28.05 \pm 1.00 
%r_AB = 22.69 \pm  0.01
%           20.85 \pm  0.01 
%           20.64 \pm 0.01
% −25.7 5.13 MMT 
}
    \label{fig:MMTJ0215-0529}
  \end{subfigure} 
  \begin{subfigure}{}
    \centering
    \includegraphics[width=8.5cm]{../light_curves/CFHQSJ0216-0455LC_20190613.png}
    \caption{The same as Fig.~\ref{fig:MMTJ0215-0529} except for CFHQS J0216-0455.}
    \label{fig:CFHQSJ0216-0455}
  \end{subfigure}
\end{figure}
